draft_yma

### 2021-12-17 draft_yma.Rmd
delete stuff i don't need

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(leaps)
library(readr)
```

@@

library(ggcorrplot)
library(ggstatsplot)
ggstatsplot::ggcorrmat(
  data = cdi_descriptive,
  type = "parametric", # parametric for Pearson, nonparametric for Spearman's correlation
  colors = c("darkred", "white", "steelblue") # change default colors
)
```

@@

```{r}
library(ggplot2)
library(ggExtra)

@@

### New tibble with transformed crm_1000 -> crm_1000_sqr
```{r}
cdi_trans = cdi_model %>% mutate(crm_1000_sqr = crm_1000^0.5) %>% select(-c(crm_1000))
```

@@

# cdi %>% filter(pop == 2300664 | pop == 396685) %>% select(cty,pop)
```

@@

@@

@@

```{r}
par(mfrow=c(2,2))
plot(fit_back)
```

@@

### Back

#### Old Method
```{r}
# residuals vs leverage plot
plot(fit_back, which = 4)
#remove outliers
cdi_trans_without = cdi_trans[-c(1, 6, 53),]
fit_without = lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_trans_without)
summary(fit_without)
```

```{r}
par(mfrow=c(2,2))
plot(fit_without)
```

### Threshold: $D_{i}>\frac{4}{n} = \frac{4}{440} = 0.009$
```{r}
cook = olsrr::ols_plot_cooksd_bar(fit_back, print_plot = TRUE)
normal = cook$data$color == "normal"
outlier = cook$data$color == "outlier"
```

```{r}
outlier_df = cdi[outlier,]
```

This gives us 21 outliers. We should consider if we want to take them all out

@@

Here's what happens when we take them all out.

```{r}
cdi_trans_without = cdi_trans[normal,]
```

@@

```{r}
fit_without = lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + pcincome + region + pbeds_1000 + density_pop, data = cdi_trans_without)

@@

# Residual performance
par(mfrow=c(2,2))
olsrr::ols_plot_resid_fit(fit_without)
olsrr::ols_plot_resid_qq(fit_without)
MASS::boxcox(fit_without)

#Cp -88.45??
olsrr::ols_mallows_cp(fit_without,trans_fit)
#BIC: 1274.534
BIC(fit_without) 
#MSE
without_summ =summary(fit_without) #1.017
mean(without_summ$residuals^2)
#VIF 
performance::check_collinearity(fit_without)
```

@@

```{r}
fit_without2 = lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + unemp + pcincome + region+ pbeds_1000 + density_pop, data = cdi_trans_without)

summary(fit_without2)

# Residual performance
par(mfrow=c(2,2))
olsrr::ols_plot_resid_fit(fit_without2)
olsrr::ols_plot_resid_qq(fit_without2)
MASS::boxcox(fit_without2)

#Cp -87.5??
olsrr::ols_mallows_cp(fit_without2,trans_fit)
#BIC: 1279.154
BIC(fit_without2)
#MSE
without2_summ =summary(fit_without2) #1.013
mean(without2_summ$residuals^2)
#VIF 
performance::check_collinearity(fit_without2) 
```

@@

cv_df = 
  cv_df %>%
  mutate(
    fit_back = map(train, ~lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + pcincome + region + pbeds_1000 + density_pop, data = .x)),
    trans_fit = map(train, ~lm(crm_1000_sqr ~ pop + pop18 + pop65+ hsgrad + bagrad + poverty + unemp + pcincome + region+ +pdocs_1000+pbeds_1000 + density_pop, data = .x)),
    fit_adjr = map(train, ~lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + unemp + pcincome + region+ pbeds_1000 + density_pop, data = .x)),
    fit_forward = map(train, ~lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + unemp + pcincome + region+ pbeds_1000 + density_pop, data = .x))) %>% 
  mutate(
    rmse_model2 = map2_dbl(fit_back, test, ~rmse(model = .x, data = .y)),
    rmse_model3 = map2_dbl(trans_fit, test, ~rmse(model = .x, data = .y)),
    rmse_model4 = map2_dbl(fit_adjr, test, ~rmse(model = .x, data = .y)),
    rmse_model5 = map2_dbl(fit_forward, test, ~rmse(model = .x, data = .y))) %>%
  mutate(
    mspe_model2 = map2_dbl(fit_back, test, ~ mean((.y$crm_1000_sqr -predict.lm(.x,.y))^2)),
    mspe_model3 = map2_dbl(trans_fit, test, ~ mean((.y$crm_1000_sqr -predict.lm(.x,.y))^2)),
    mspe_model4 = map2_dbl(fit_adjr, test, ~ mean((.y$crm_1000_sqr -predict.lm(.x,.y))^2)),
    mspe_model5 = map2_dbl(fit_forward, test, ~ mean((.y$crm_1000_sqr -predict.lm(.x,.y))^2))
  ) %>% 
  mutate(
    res_model2 = map(fit_back, broom::glance %>% as.data.frame),
    res_model3 = map(trans_fit, broom::glance %>% as.data.frame),
    res_model4 = map(fit_adjr, broom::glance %>% as.data.frame),
    res_model5 = map(fit_forward, broom::glance %>% as.data.frame)) %>%
  unnest(res_model2, res_model3, res_model4, res_model5) %>%
  dplyr::select(rmse_model2,rmse_model3,rmse_model4,rmse_model5,
                mspe_model2,mspe_model3,mspe_model4,mspe_model5,
                value.adj.r.squared,value.adj.r.squared1,value.adj.r.squared2,value.adj.r.squared3) %>%
  rename(adjR_model2 = value.adj.r.squared,
         adjR_model3 = value.adj.r.squared1,
         adjR_model4 = value.adj.r.squared2,
         adjR_model5 = value.adj.r.squared3)

@@

## Plot the violin plot
```{r warning=FALSE}
unnest_cd_df = cv_df %>%
  pivot_longer(rmse_model2:adjR_model5, 
               names_pattern = "(.*)(......)$", 
               names_to = c("limit", "model")) %>% 
  mutate(limit=ifelse(limit=="", "value", limit)) %>%
  pivot_wider(id_cols = model, 
              names_from = limit, 
              values_from = value, 
              names_repair = "check_unique") %>% 
  unnest(c(rmse_, adjR_)) %>%
  rename(rmse = rmse_,
         adjR = adjR_)
unnest_cd_df %>% ggplot(aes(x = model, y = rmse)) + geom_violin() 
unnest_cd_df %>% ggplot(aes(x = model, y = adjR)) + geom_violin() 
```

## backward by hand

```{r}
# No docs
step1 = update(trans_fit, . ~ . -pdocs_1000)
summary(step1)

# No pop65
step2 = update(step1, . ~ . -pop65)
summary(step2)

# No unemp
step3 = update(step2, . ~ . -unemp)
summary(step3)

step4 = update(step3, . ~ . -hsgrad)
summary(step4)

mult.fit.final = lm(crm_1000^0.5 ~ pop + pop18 + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_model)
summary(mult.fit.final)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(leaps)
library(readr)
library(flexmix)
```

@@

library(ggcorrplot)
library(ggstatsplot)
ggstatsplot::ggcorrmat(
  data = cdi_descriptive,
  type = "parametric", 
  colors = c("darkred", "white", "steelblue") # change default colors
)

ggcorrplot(cor(cdi_descriptive), type = "upper",
   lab = TRUE)
```

@@

```{r}
library(ggplot2)
library(ggExtra)
```

@@

### New tibble with transformed y
```{r}
cdi_trans = cdi_model %>% mutate(crm_1000_sqr = crm_1000^0.5) %>% select(-c(crm_1000))
```

@@

# cdi %>% filter(pop == 2300664 | pop == 396685) %>% select(cty,pop)

cdi_trans_without1 = cdi_tans[]
```

@@

```{r}
fit_back_int = lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + pcincome + region + pbeds_1000 + density_pop + pcincome*poverty, data = cdi_trans)
summary(fit_back_int)

olsrr::ols_plot_resid_fit(fit_back_int)
olsrr::ols_plot_resid_qq(fit_back_int)
MASS::boxcox(fit_back_int)
#Cp
olsrr::ols_mallows_cp(fit_back_int,trans_fit) #13.94
#adjr 0.5701

BIC(fit_back_int) #1435.05

back_int_summ =summary(fit_back_int) #1.331
mean(back_int_summ$residuals^2) #1.2598

performance::check_collinearity(fit_back_int)

fit_back_int_without = lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + pcincome + region + pbeds_1000 + density_pop + pcincome*poverty, data = cdi_trans_without)

summary(fit_back_int_without) #adjr 0.5658

# Residual performance
par(mfrow=c(2,2))
olsrr::ols_plot_resid_fit(fit_back_int_without)
olsrr::ols_plot_resid_qq(fit_back_int_without)
MASS::boxcox(fit_back_int_without)

#Cp -38.65??
olsrr::ols_mallows_cp(fit_back_int_without,trans_fit)
#BIC: 1401.441
BIC(fit_back_int_without) 
#MSE
back_int_without_summ =summary(fit_back_int_without) #1.18
mean(back_int_without_summ$residuals^2)
#VIF 
performance::check_collinearity(fit_back_int_without)
```

@@

#### AIC

```{r}
AIC(fit_back) # 1400.399
AIC(fit_forward) #1404.519
AIC(fit_both) #1400.399
AIC(fit_adjr) # 1400.889
AIC(fit_Cp) # 1400.399
```

@@

@@

```{r}
olsrr::ols_plot_cooksd_bar(strp_back, print_plot = TRUE)
#remove observations whose cook's D > 0.5
cdi_trans_without = cdi_trans[-c(1, 6),]
```

@@

@@

```{r}
fit_back_without = lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + pcincome + region + pbeds_1000 + density_pop, data = cdi_trans_without)

@@

# Residual performance
par(mfrow=c(2,2))
olsrr::ols_plot_resid_fit(fit_back_without)
olsrr::ols_plot_resid_qq(fit_back_without)
MASS::boxcox(fit_back_without)
```

Build the without model with **trans_fit** (full model)

```{r}
trans_fit_without = lm(crm_1000_sqr ~., data = cdi_trans_without)

summary(trans_fit_without)

# Residual performance
par(mfrow=c(2,2))
olsrr::ols_plot_resid_fit(trans_fit_without)
olsrr::ols_plot_resid_qq(trans_fit_without)
MASS::boxcox(trans_fit_without)
```

@@

```{r}
fit_adjr_without = lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + unemp + pcincome + region+ pbeds_1000 + density_pop, data = cdi_trans_without)

summary(fit_adjr_without)

# Residual performance
par(mfrow=c(2,2))
olsrr::ols_plot_resid_fit(fit_adjr_without)
olsrr::ols_plot_resid_qq(fit_adjr_without)
MASS::boxcox(fit_adjr_without)
```

#### Cp for models fit without outlier

```{r}
olsrr::ols_mallows_cp(fit_back_without,trans_fit_without) # 7.047
olsrr::ols_mallows_cp(trans_fit_without,trans_fit_without)# 11
olsrr::ols_mallows_cp(fit_adjr_without,trans_fit_without) # 7.102
```

#### AIC

```{r}
AIC(fit_back_without) # 1371.373
AIC(trans_fit_without) #1375.258
AIC(fit_adjr_without) # 1371.363
AIC(fit_back_int_without) #1344.376
```

```{r}
BIC(fit_back_without) #1424.441
BIC(trans_fit_without) #1440,573
BIC(fit_adjr_without) # 1428.514
BIC(fit_back_int_without) #1401.527
```

```{r}
back_without_summ =summary(fit_back_without) #1.2633
mean(back_without_summ$residuals^2)

trans_without_summ =summary(trans_fit_without) #1.2572
mean(trans_without_summ$residuals^2)

adjr_without_summ =summary(fit_adjr_without) #1.2575
mean(adjr_without_summ$residuals^2)

int_without_summ =summary(fit_back_int_without) #1.18
mean(int_without_summ$residuals^2)

@@

cv_df = 
  cv_df %>%
  mutate(
    fit_back = map(train, ~lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + pcincome + region + pbeds_1000 + density_pop, data = .x)),
    trans_fit = map(train, ~lm(crm_1000_sqr ~ pop + pop18 + pop65+ hsgrad + bagrad + poverty + unemp + pcincome + region+ +pdocs_1000+pbeds_1000 + density_pop, data = .x)),
    fit_adjr = map(train, ~lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + unemp + pcincome + region+ pbeds_1000 + density_pop, data = .x)),
    fit_back_int_without = map(train,~lm(crm_1000_sqr ~ pop + pop18 + hsgrad + bagrad + poverty + pcincome + region + pbeds_1000 + density_pop + pcincome*poverty, data = .x))
    ) %>% 
  mutate(
    rmse_back = map2_dbl(fit_back, test, ~rmse(model = .x, data = .y)),
    rmse_full = map2_dbl(trans_fit, test, ~rmse(model = .x, data = .y)),
    rmse_adjr = map2_dbl(fit_adjr, test, ~rmse(model = .x, data = .y)),
    rmse_bain = map2_dbl(fit_back_int_without, test, ~rmse(model = .x, data = .y))) %>%
  mutate(
    mspe_back = map2_dbl(fit_back, test, ~ mean((.y$crm_1000_sqr -predict.lm(.x,.y))^2)),
    mspe_full = map2_dbl(trans_fit, test, ~ mean((.y$crm_1000_sqr -predict.lm(.x,.y))^2)),
    mspe_adjr = map2_dbl(fit_adjr, test, ~ mean((.y$crm_1000_sqr -predict.lm(.x,.y))^2)),
    mspe_bain = map2_dbl(fit_back_int_without, test, ~ mean((.y$crm_1000_sqr -predict.lm(.x,.y))^2))
  ) %>% 
  mutate(
    res_back = map(fit_back, broom::glance %>% as.data.frame),
    res_full = map(trans_fit, broom::glance %>% as.data.frame),
    res_adjr = map(fit_adjr, broom::glance %>% as.data.frame),
    res_bain = map(fit_back_int_without, broom::glance %>% as.data.frame),
    ) %>%
  unnest(res_back, res_full, res_adjr, res_bain) %>%
  dplyr::select(rmse_back,rmse_full,rmse_adjr,rmse_bain,
                mspe_back,mspe_full,mspe_adjr,mspe_bain,
                value.adj.r.squared,value.adj.r.squared1,value.adj.r.squared2,value.adj.r.squared3) %>%
  rename(adjR_back = value.adj.r.squared,
         adjR_full = value.adj.r.squared1,
         adjR_adjr = value.adj.r.squared2,
         adjR_bain = value.adj.r.squared3)

@@

## Plot the violin plot
```{r warning=FALSE}
unnest_cd_df = cv_df %>%
  pivot_longer(rmse_back:adjR_bain, 
               names_pattern = "(.*)(....)$", 
               names_to = c("limit", "model")) %>% 
  mutate(limit=ifelse(limit=="", "value", limit)) %>%
  pivot_wider(id_cols = model, 
              names_from = limit, 
              values_from = value, 
              names_repair = "check_unique") %>% 
  unnest(c(rmse_, adjR_)) %>%
  rename(rmse = rmse_,
         adjR = adjR_)
unnest_cd_df %>% ggplot(aes(x = model, y = rmse)) + geom_violin() 
unnest_cd_df %>% ggplot(aes(x = model, y = adjR)) + geom_violin() 
```

```{r}
olsrr::ols_plot_resid_qq(fit_back_int_without)
olsrr::ols_plot_resid_fit(fit_back_int_without)
MASS::boxcox(fit_back_int_without)
```

```{r}
locfit::cp(fit_back_without)
```

```{r}
models1 <- regsubsets(crm_1000_sqr ~., data = cdi_trans_without,nvmax = 12)
res_sum1 = summary(models1)

par(mfrow=c(1,2))
plot(1:12, res_sum1$cp, xlab="No of parameters", ylab="Cp Statistic")
plot(1:12, res_sum1$adjr2, xlab="No of parameters", ylab="Adj R2")
```
